Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2016-03-03 draft.tex
put plainpages=false back and add pageanchor=false to overcome pageanchor error
remove lowercase state variables throughout appendix

\documentclass[11pt,letterpaper, notitlepage]{article}
\usepackage{epsf,graphicx,psfrag}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{fullpage}
\usepackage[reqno]{amsmath}
\usepackage{endnotes}
\usepackage{natbib}
\usepackage{amsfonts}
\usepackage{amssymb,enumerate}
\usepackage{dcolumn}
\usepackage{verbatim}
%\usepackage{hypertex}
\usepackage[pdftex, bookmarks, colorlinks=true, plainpages = false, citecolor = blue, urlcolor = blue, filecolor = blue, breaklinks]{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[hmargin=3.0cm,vmargin=3.0cm]{geometry}
%\usepackage{geometry}
\usepackage{nicefrac}
\usepackage{pdfsync}
\usepackage{url}
\usepackage{pst-all}
\usepackage{pdflscape}
\usepackage{rotating}
\usepackage[T1]{fontenc}
\usepackage[sc]{mathpazo}
\usepackage{graphicx,verbatim,scalefnt}

@@

\date{\today}
\begin{document}
\begin{titlepage}
\maketitle
\thispagestyle{empty}
%\center{This article is a working paper and is subject to future revision during the peer-review process. The authors welcome any comments, and may be reached by e-mail at benjamin.a.graham@usc.edu.}

@@

\end{titlepage}
\setcounter{page}{1}

@@

Player $c$ would be able to induce the secessionists to play Cede---e.g. counter an addition to $q_s^t$ with an investment to $l_s^t$---as long as $R_c^{RU} = \frac{\beta + R_c^{SQ}}{1 -\de} > Q_s^{t-1} -\mu + R_p^t - L_s^{t-1}$.\footnote{Here we assume that the payoff relationship at $t$ is such that ceding is better than fighting. If this relationship is reversed, similar analysis and results hold.} For this to work, the investment required of player $c$ must be no more than the gain player $c$ receives from investing.

On the other hand, if $\frac{\beta + R_c^{SQ}}{1 -\de} \leq Q_s^{t-1} -\mu + R_p^t - L_s^{t-1}$, the patron's investment creates a large enough difference in $Q_s^t - L_s^t$ (net of player $c$'s investment) so that player $c$ will not find contesting the status quo to be in its interest. Whenever the status quo will be the outcome in this way, $c$ maximizes its utility by choice of $R_c^{SQ} =0$.

@@

If $\frac{\nu}{1-\de} < L_g^{t-1} + R_p^t - Q_g^{t-1}$, the patron's investment in $l_g^t$ creates a large enough difference in $L_s^t - Q_s^t$ (net of player $c$'s investment) so that player $c$ will not find it worthwhile to re-establish the status quo outcome.

On the other hand, player $c$ would be willing to counter whatever investment player $p$ makes to try to induce recognition---e.g. counter an addition to $l_g^t$ with an investment to $q_g^t$---as long as $\frac{\nu}{1-\de} \geq L_g^{t-1} + R_p^t - Q_g^{t-1}$.\footnote{As in the proof of Lemma 2, we have assumed that the payoff relationship at $t$ is such that ceding is better than fighting. If this relationship is reversed, similar analysis and results hold.}

@@

On the other hand, player $c$ would be willing to counter whatever investment player $p$ makes to try to induce fighting---e.g. counter an addition to $\omega_s^t$ with an investment to $q_s^t$---as long as $\frac{\nu p_s - \beta (1-p_s)}{1 -\de}  \geq \omega_s^t\left(R_p^t\right) - Q_s^t$.

>>>>

\documentclass[11pt,letterpaper, notitlepage]{article}
\usepackage{epsf,graphicx,psfrag}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{fullpage}
\usepackage[reqno]{amsmath}
\usepackage{endnotes}
\usepackage{natbib}
\usepackage{amsfonts}
\usepackage{amssymb,enumerate}
\usepackage{dcolumn}
\usepackage{verbatim}
%\usepackage{hypertex}
\usepackage[pdftex, bookmarks, colorlinks=true, plainpages=false, citecolor = blue, urlcolor = blue, filecolor = blue, breaklinks]{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[hmargin=3.0cm,vmargin=3.0cm]{geometry}
%\usepackage{geometry}
\usepackage{nicefrac}
\usepackage{pdfsync}
\usepackage{url}
\usepackage{pst-all}
\usepackage{pdflscape}
\usepackage{rotating}
\usepackage[T1]{fontenc}
\usepackage[sc]{mathpazo}
\usepackage{graphicx,verbatim,scalefnt}

@@

\date{\today}
\begin{document}
\hypersetup{pageanchor=false}
\begin{titlepage}
\maketitle
\thispagestyle{empty}
%\center{This article is a working paper and is subject to future revision during the peer-review process. The authors welcome any comments, and may be reached by e-mail at benjamin.a.graham@usc.edu.}

@@

\end{titlepage}
\hypersetup{pageanchor=true}
\setcounter{page}{1}

@@

Player $c$ would be able to induce the secessionists to play Cede---e.g. counter an addition to $Q_s^{t-1}$ with an investment to $L_s^{t-1}$---as long as $R_c^{RU} = \frac{\beta + R_c^{SQ}}{1 -\de} > Q_s^{t-1} -\mu + R_p^t - L_s^{t-1}$.\footnote{Here we assume that the payoff relationship at $t$ is such that ceding is better than fighting. If this relationship is reversed, similar analysis and results hold.} For this to work, the investment required of player $c$ must be no more than the gain player $c$ receives from investing.

On the other hand, if $\frac{\beta + R_c^{SQ}}{1 -\de} \leq Q_s^{t-1} -\mu + R_p^t - L_s^{t-1}$, the patron's investment creates a large enough difference in the secessionist's payoffs from the status quo versus ceding (net of player $c$'s investment) so that player $c$ will not find contesting the status quo to be in its interest. Whenever the status quo will be the outcome in this way, $c$ maximizes its utility by choice of $R_c^{SQ} =0$.

@@

If $\frac{\nu}{1-\de} < L_g^{t-1} + R_p^t - Q_g^{t-1}$, the patron's investment to augment $L_g^{t-1}$ creates a large enough difference in the secessionists' payoffs of ceding versus the status quo (net of player $c$'s investment) so that player $c$ will not find it worthwhile to re-establish the status quo outcome.

On the other hand, player $c$ would be willing to counter whatever investment player $p$ makes to try to induce recognition---e.g. counter an addition to $L_g^{t-1}$ with an investment to augment $Q_g^{t-1}$---as long as $\frac{\nu}{1-\de} \geq L_g^{t-1} + R_p^t - Q_g^{t-1}$.\footnote{As in the proof of Lemma 2, we have assumed that the payoff relationship at $t$ is such that ceding is better than fighting. If this relationship is reversed, similar analysis and results hold.}

@@

On the other hand, player $c$ would be willing to counter whatever investment player $p$ makes to try to induce fighting---e.g. counter an addition to $\omega_s^t$ with an investment to augment $Q_s^{t-1}$---as long as $\frac{\nu p_s - \beta (1-p_s)}{1 -\de}  \geq \omega_s^t\left(R_p^t\right) - Q_s^t$.
